---
title: "ROS burst line graph with facets"
author: "Marijn Knip"
date: "2/6/2018"
output:
  html_document: default
  pdf_document: default
---

```{r setup}
knitr::opts_chunk$set(echo = TRUE)

rm(list=ls())

## install libraries below, if needed

## install.packages("ggplot2")
## install.packages("rstudioapi")
## install.packages("tidyr")
## install.packages("doBy")
## install.packages("dplyr")
##install.packages("gridExtra")

library(ggplot2)
##library(rstudioapi)
library(tidyr)
library(doBy)
##library(dplyr)
##library(gridExtra)

```

## First, data will be read from the directory where this file is located and wide-format csv will be converted to longformat.
Because I'm an idiot, i've manually inserted columns in the data that guide the faceting and X-axis. This should be automated as soon as i know more R.

```{r}
##set working directory to location of this .R file and read datafile
## This isn't necessary and doesn't work with Knit
##setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
            widedata <- read.table("data - Figure S1.csv", ##change to your *.csv
                   header = T,
                   sep = ";",
                   dec = "."
)

        
## convert data from wide to long format

        longdata <- gather(widedata,Timename,Measurement, Sample1:Sample10,factor_key=TRUE)
        longdata$Timename <- NULL
        filterlongdata <- longdata %>% drop_na()
        
## summarizing data
data <- summaryBy(.~Time+Construct, data=filterlongdata, FUN=c(length,mean,sd))

legendname1=  "Mock treatment"
legendname2=  "Flg22"

```

## Including Plots

Here's the basic plot that's being generated. Not how i'm using  stat_smooth instead of geom_line. Fits a polynomial on the points; looks nice.

```{r, echo=FALSE}

##drawing plot > Mean values incl. stdev.
#line graph with dots, slightly transparent (alpha)
# set position dodge to move data pounts slightly
p1 <- ggplot(data, aes(x=Time, y=Measurement.mean, color=Construct)) + 
    stat_smooth(aes(x = Time, y = Measurement.mean), method = "gam",
              formula = y ~ s(x, k = 12), se = FALSE)+
    geom_point(size=2, alpha = 0.5, position = position_dodge(0.05))+
  ##Blue/red--Purple,Blues,Greens::
    scale_color_manual(labels = c(legendname1,legendname2),
                       values=c("#2b83ba","#d7191c"))+
    geom_errorbar(aes(ymin=Measurement.mean-Measurement.sd, ymax=Measurement.mean+Measurement.sd), width=0.2, alpha = 0.6)
p1
```

## Adding labels and facetting
The plot from this data contains three facets.

```{r}


##Changing the labels
p2 <-  p1 + labs(title = "", subtitle = "", color="Constructs") + 
            ylab("Luminescence(AU)") 
p2

```

## Formatting the rest of the plot
Set font sizes, rotation, spacing of facets, legend, line thickness etc...

```{r}
p3 <- p2 +        theme(axis.text = element_text(size = 14),
                  panel.spacing = unit(1.5, "lines"),
                  legend.key = element_rect(fill = "white", colour = "black"),
                  legend.text = element_text(size = 14, angle = 0, colour = "Black"),
                  legend.title = element_text(face = "bold", size = 14, angle = 0, colour = "Black"),
                  legend.background = element_rect(fill = "white"),
                  legend.position = "bottom",
                  legend.key.size = unit(1.5, 'lines'),
                  panel.grid.major = element_line(colour = "grey96"),
                  panel.grid.minor = element_blank(),
                  panel.background = element_rect(fill = "white"), 
                  panel.border = element_rect(colour = "black",fill=NA, size=1),
                  plot.title = element_text(hjust=0.5, face = "bold", size = 20, angle = 0, colour = "Black"),
                  plot.subtitle = element_text(hjust=0.5, face = "italic", size = 14, angle = 0, colour = "Black"),
                  axis.title = element_text(size = 14, angle = 0, colour = "Black"),
                  axis.text.x = element_text(size = 14, angle = 0, colour = "grey20", hjust=0.5, vjust=0.8),
                  strip.text = element_text(size = 14, angle = 0, colour = "Black"))+
                  scale_x_continuous("Time",breaks= c(0,3,6,9,12),
                                labels = c("00:00", "07:30", "18:30","29:30", "40:30"))
p3
```

## Output your plot
Generate files from the plot you made.

```{r}

# save to file
ggsave(filename = "ROSburst-line-notitle.png",plot = p3,width = 8,height = 6,dpi = 600)

##if you want a PDF
##ggsave(filename = "ROSburstBox.pdf",plot = p3,width = 12,height = 6,dpi = 600) 

```
Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
