---
title: "Generic Ion Leakage"
author: "Marijn Knip"
date: "23 november 2017"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---

```{r setup, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

## Simple Line graph for Ion Leakage experiments

This script generates simple line graphs for data generated in an ion-leakage experiment using leaf discs.
This script reads *.csv files in long format located in the same folder as the script file.
In this section different elements in the output figure can be set.

```{r, echo=off}
## install libraries below, if needed
## install.packages("ggplot2")
## install.packages("doBy")
library(ggplot2)
library(doBy)
library(ggpubr)
library(tidyr)

  iondata <- read.table("data - Figure 3A.csv", ##change to your *.csv
                     header = T,
                     sep = ";",
                     dec = ","
)

##insert plot title, axis titles, legend text etc. here

plottitle=    "Rx1-induced DNA-damage"
plotsubtitle= "virulent vs. avirulent coat protein"
legendtitle=  "Constructs"
xaxislabel=   "Time after DEX-induction (hrs)"
yaxislabel=   "Fluorescence ratio (Fluorescein/DAPI)"
legendname1=  "DEX::CP105"
legendname2=  "DEX::CP106"


##summarizing data
iondata$Time <-as.factor(iondata$Time)
iondata$Fluorescence <-as.numeric(iondata$Fluorescence)

data <- summaryBy(Fluorescence ~ Time + Construct, data=iondata, FUN=c(length,mean,sd))

data$Construct <- as.character(data$Construct)
data$Construct[data$Construct == "CP105"] <- "DEX::CP105"
data$Construct[data$Construct == "CP106"] <- "DEX::CP106"

data$Construct <- as.factor(data$Construct)

summary(data)

```

## Building the plot
In the section below is the code to generate the simple plot:

```{r echo=off}
## drawing plot > Mean values incl. stdev.
#  line graph with dots, slightly transparent (alpha)
#  set position dodge to move data pounts slightly
## Using scale_colour_manual (matching brewer "spectral" colour), as using only two colors brewer with spectral palette doesn't give red/blue 
pd <- position_dodge(0.02)

p1 <- ggplot(data, aes(x=Time, y=Fluorescence.mean, group=Construct)) + 
        geom_line(aes(color=Construct))+
        geom_point(aes(shape=Construct, color=Construct),
                   size=3, 
                   alpha = 0.4, 
                   position = pd)+
   geom_errorbar(aes(ymin=Fluorescence.mean-Fluorescence.sd,
                       ymax=Fluorescence.mean+Fluorescence.sd),
                                  width=0.2, 
                                  position=pd, 
                                  alpha = 0.4)+
   scale_color_manual(values = c("#2b83ba","#d7191c")) 
p1
```



```{r echo=off}
  
  
p2 <- p1+stat_compare_means(data=iondata, aes(x=Time, y=Fluorescence),
                           method="wilcox",
                           label = "p.signif",
                           show.legend=FALSE,
                           size=6
                          ## label.y=c(35,40,55,90,145)
                         )
                
        
plot(p2)
```

## Plot design
Now the plot is generated we improve the design:


```{r}
#enhancing plot design
#setting labels and titles
p3 <- p2 + labs(x=xaxislabel, 
                y=yaxislabel,
                fill=legendtitle
         #       title=plottitle,
        #        subtitle=plotsubtitle
               ) +
        scale_y_continuous(limits=c(0, 1.2)
                            )
               
#changing Theme
p4 <- p3 +theme(
  plot.title = element_text(hjust = 0.5 , color="black", size=14, face="bold"),
  plot.subtitle = element_text(hjust = 0.5 , color="black", size=14, face="italic"),
  axis.title.x = element_text(color="black", size=14, face="plain"),
  axis.title.y = element_text(color="black", size=14, face="plain"),
  panel.background = element_rect(fill = "white",
                                  colour = "white",
                                  size = 0.5, linetype = "solid"),
  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                  colour = "#f9f9f9"), 
  panel.grid.minor = element_blank(),
  panel.border = element_rect(colour = "black", fill=NA, size=1),
  text = element_text(size=14, face = "plain"), 
  legend.key = element_blank(),  ## Get rid of the legend box 
  legend.title = element_text(size = 14, face="bold"),
  legend.text = element_text(size = 14, face="italic"),
  legend.position = "bottom",
  legend.background = element_rect(fill=alpha(0.0001))
)
plot(p4)
```




```{r}

# save to file
ggsave(filename = "Tunel-combo-notitle.png",plot = p4,width = 8,height = 6,dpi = 900)

##if you want a PDF
ggsave(filename = "ROSburstBox.pdf",plot = p4,width = 8,height = 4,dpi = 600) 

```