---
title: "Generic Ion Leakage"
author: "Marijn Knip"
date: "23 november 2017"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---

```{r setup, include=FALSE}
rm(list=ls())
library(knitr)
knitr::opts_chunk$set(echo = TRUE)
```

## Simple Line graph for Ion Leakage experiments

This script generates simple line graphs for data generated in an ion-leakage experiment using leaf discs.
This script reads *.csv files in long format located in the same folder as the script file.
In this section different elements in the output figure can be set.

```{r, echo=off}
## install libraries below, if needed
## install.packages("ggplot2")
## install.packages("doBy")
library(ggplot2)
library(doBy)
library(ggpubr)
library(tidyr)

  iondata <- read.table("data - Figure 4A.csv", ##change to your *.csv
                     header = T,
                     sep = ";",
                     dec = "."
)

##insert plot title, axis titles, legend text etc. here
plottitle=    ""
plotsubtitle= ""
legendtitle=  "Constructs"
xaxislabel=   "Time after DEX-induction (hrs)"
yaxislabel=   "Conductivity (\U03BCS/m)"
legendname1=  "DEX::CP105"
legendname2=  "DEX::CP106"


##summarizing data
iondata$Leaf <- NULL
iondata$Timepoint <-as.factor(iondata$Timepoint)

iondata$Construct <- as.character(iondata$Construct)
iondata$Construct[iondata$Construct == "CP105"] <- "DEX::CP105"
iondata$Construct[iondata$Construct == "CP106"] <- "DEX::CP106"

iondata$Construct <- as.factor(iondata$Construct)

data <- summaryBy(Conductivity ~ Timepoint + Construct, data=iondata, FUN=c(length,mean,sd))



summary(data)

```

## Building the plot
In the section below is the code to generate the simple plot:

```{r echo=off}
## drawing plot > Mean values incl. stdev.
#  line graph with dots, slightly transparent (alpha)
#  set position dodge to move data pounts slightly
## Using scale_colour_manual (matching brewer "spectral" colour), as using only two colors brewer with spectral palette doesn't give red/blue 
pd <- position_dodge(0.00)

p1 <- ggplot(data, aes(x=Timepoint, y=Conductivity.mean, color=Construct, group=Construct)) + 
        geom_point(aes(shape=Construct),
                   size=3, 
                   alpha = 0.4, 
                   position = pd)+
        geom_line()+
        scale_color_manual(values = c("#2b83ba","#d7191c"))
        
plot(p1)
```
```{r, echo=off}

p2 <- p1 + geom_errorbar(data=data, 
                         aes(ymin=Conductivity.mean-Conductivity.sd,ymax=Conductivity.mean+Conductivity.sd), 
                         width=0.2, 
                         position=pd,
                         alpha=0.4) +
           stat_compare_means(data=iondata, 
                        aes(x=Timepoint, y=Conductivity),
                        method="wilcox.test",
                        label = "p.signif", 
                        label.y=c(35,40,55,90,145),
                        show.legend=FALSE)
p2 
 
```

## Plot design
Now the plot is generated we improve the design:


```{r}
#enhancing plot design
#setting labels and titles
p3 <- p2 + labs(x=xaxislabel, 
                y=yaxislabel,
                color=legendtitle,
                shape=legendtitle,
                title=plottitle,
                subtitle=plotsubtitle
               ) +
          scale_y_continuous(limits=c(0, 150),
                             breaks=seq(0,150,25),
                             expand = c(0, 0))
               
#changing Theme
p4 <- p3 +theme(
  plot.title = element_text(hjust = 0.5 , color="black", size=24, face="bold"),
  plot.subtitle = element_text(hjust = 0.5 , color="black", size=16, face="italic"),
  axis.title.x = element_text(color="black", size=14, face="plain"),
  axis.title.y = element_text(color="black", size=14, face="plain"),
  panel.background = element_rect(fill = "white",
                                  colour = "white",
                                  size = 0.5, linetype = "solid"),
  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                  colour = "#f9f9f9"), 
  panel.grid.minor = element_blank(),
  panel.border = element_rect(colour = "black", fill=NA, size=1),
  text = element_text(size=14, face = "plain"), 
  legend.key = element_blank(),  ## Get rid of the legend box 
  legend.title = element_text(size = 14, face="bold"),
  legend.text = element_text(size = 14, face="italic"),
  legend.position="bottom",
  legend.background = element_rect(fill=alpha(0.0001))
)
plot(p4)
```

```{r}
#enhancing plot design
#setting labels and titles
p3 <- p2 + scale_y_continuous(limits=c(0, 150),
                             breaks=seq(0,150,25),
                             expand = c(0, 0))
               
#changing Theme
p4 <- p3 +theme(
  plot.title = element_text(hjust = 0.5 , color="black", size=24, face="bold"),
  plot.subtitle = element_text(hjust = 0.5 , color="black", size=16, face="italic"),
  axis.title.x = element_blank(),
  axis.title.y = element_blank(),
  panel.background = element_rect(fill = "white",
                                  colour = "white",
                                  size = 0.5, linetype = "solid"),
  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                  colour = "#f9f9f9"), 
  panel.grid.minor = element_blank(),
  panel.border = element_rect(colour = "black", fill=NA, size=1),
  text = element_text(size=14, face = "plain"), 
  legend.key = element_blank(),  ## Get rid of the legend box 
  legend.title = element_blank(),
  legend.text = element_blank(),
  legend.position="bottom",
  legend.background = element_rect(fill=alpha(0.0001))
)
plot(p4)
```
```{r}

# save to file
ggsave(filename = "Ion-leakage-line-narrow-notitle.pdf",plot = p4,width = 8,height = 6,dpi = 600)
ggsave(filename = "Ion-leakage-line-narrow-notitle-new.svg",plot = p4,width = 8,height = 6,dpi = 600)
##if you want a PDF
##ggsave(filename = "ROSburstBox.pdf",plot = p3,width = 12,height = 6,dpi = 600) 

```